Update Meeting: 14-06-2021

### 2021-06-18 analysis/update_meeting_14_06_2021.Rmd
wflow_publish(c("analysis/index.Rmd", "analysis/update_meeting_14_06_2021.Rmd"))

@@

>>>>

```{r setup, include = FALSE}

options(scipen=999)
source("code/settings.R")
load("summary.Rdata")
library(DT)
library(knitr)

```

```{r, echo=FALSE,include = FALSE}
# You need this code to conduct the magic dependences attaching...
DT::datatable(matrix())
```

@@

## Results.

### Traits analyzed.

```{r traits, echo = FALSE}

DT::datatable(traits, width = "100%")

```

### Summary Heterogeneity between sexes.

```{r sex_het, echo = FALSE}

reduced_mr_summary <- calc_mr_sex_het %>% dplyr::select(trait_ID, trait_description, 
                                                        exposure_sex, N_snps,"IVW/Wald_summary","IVW/Wald_pval", 
                                                        "MR_meta_est", "MR_meta_pval", "sex_het")

DT::datatable(reduced_mr_summary, width = "100%")

```

### Testing discrepancy amongst bins.

```{r mr_summary_age, echo = FALSE}

mr_summary_age_reduced <- mr_summary_age %>% dplyr::select(trait_ID, exposure_sex, Q_stat, Q_pval)
DT::datatable(mr_summary_age_reduced, width = "100%")

mr_summary_tt_reduced <- mr_summary_tt %>% dplyr::select(trait_ID, exposure_sex, Q_stat, Q_pval)
DT::datatable(mr_summary_tt_reduced, width = "100%")

```
